Secontrails plots

### 2022-02-15 R/DraftFunctions.Rmd
In loggingsimulation function + slope criteria in treefelling
Package renaming

```{r}
library(EcoFoG)
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
library(nngeo)
library(raster)
library(topoDistance)
library(BIOMASS)
```

@@

# LoggingSimulationOutputs <- Rslt
# usethis::use_data(LoggingSimulationOutputs)

@@

# Data loading
```{r}
data(Paracou6_2016) #data inventory in the global environment
data(ForestZoneVolumeParametersTable) # The volume parameters data in the global environment
# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "Maria")) # the test inventory in the global environment
data(ParamCrownDiameterAllometry)
data(SpeciesCriteria)
```
```{r}
lapply(Paracou6_2016, class) #give the class of all the data variables
```

>>>>

```{r}
library(EcoFoG)
library(LoggingLab)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
library(schoolmath)
library(ggplot2)
library(reshape)
library(sf)
library(nngeo)
library(raster)
library(topoDistance)
library(BIOMASS)
```

@@

# LoggingSimulationOutputs <- Rslt
# usethis::use_data(LoggingSimulationOutputs, overwrite = TRUE)

# LoggingSimulationOutputs_iter <- Rslt
# usethis::use_data(LoggingSimulationOutputs_iter, overwrite = TRUE)

@@

# Data loading
```{r}
data(Paracou6_2016) #data inventory in the global environment
data(ForestZoneVolumeParametersTable) # The volume parameters data in the global environment
# load(system.file("extdata", "BrokenParacou6_2016.rda", package = "LoggingLab")) # the test inventory in the global environment
data(ParamCrownDiameterAllometry)
data(SpeciesCriteria)
```
```{r}
lapply(Paracou6_2016, class) #give the class of all the data variables
```

### 2022-02-15 R/Secontrails plots.Rmd
Package renaming

# Libraries
```{r}
library(Maria)
library(ggplot2)
library(sf)
library(dplyr)
library(tibble)
```

@@

write.csv2(NewInventory, "C:/Users/Vincyane/Documents/Maria-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple

>>>>

# Libraries
```{r}
library(LoggingLab)
library(ggplot2)
library(sf)
library(dplyr)
library(tibble)
```

@@

write.csv2(NewInventory, "C:/Users/Vincyane/Documents/LoggingLab-pictures/ParacouP6_EFI3.csv") #  D:/VSC Kourou/Dataexemple
